### 2019-10-01 conflog.tex

We propose the conference be held on either of the following dates: 
\begin{enumerate}
	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
\end{enumerate}
We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools. Additionally, mid-April offers pleasant, mild, weather in Champaign. The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April. The Illinois Mom's Association has not yet announced their 2021 dates but, to avoid potential conflict, we suggest two dates. In the event that both of these dates are unavailable our backup date is 
\begin{itemize}
	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
\end{itemize}
This is a backup date because Easter falls on that Sunday. In general, this 
should be avoided. In this case we found that holding the conference at the end 
of April would conflict with finals for students and holding it earlier in 
March would conflict with several spring breaks as well as having potentially 
poorer weather. \textbf{A detailed graphical conflict schedule can be found in Appendix 
\ref{appendix:schedule} on page \pageref{appendix:schedule}.}

@@

\subsubsection{Illini Union}
After the career fair is taken down on Saturday, the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in round tables. Catering will be provided by University Catering which allows us to avoid the 20\% gratuity for services. A floorplan for the Illini Rooms in round tables is available in Appendix D.\\

>>>>

We propose the conference be held on either of the following dates: 
\begin{enumerate}
	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
\end{enumerate}
We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools. Additionally, mid-April offers pleasant, mild weather in Champaign. The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April. The Illinois Mom's Association has not yet announced their 2021 dates but, to avoid potential conflict, we suggest two dates. In the event that both of these dates are unavailable our backup date is 
\begin{itemize}
	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
\end{itemize}
This is a backup date because Easter falls on that Sunday. In general, this 
should be avoided. In this case we found that holding the conference at the end 
of April would conflict with finals for students and holding it earlier in 
March would conflict with several spring breaks as well as having potentially 
poorer weather. \textbf{A detailed graphical conflict schedule can be found in Appendix 
\ref{appendix:schedule} on page \pageref{appendix:schedule}.}

@@

\subsubsection{Illini Union}
After the career fair is taken down on Saturday, the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in round tables. Catering will be provided by University Catering which allows us to avoid the 20\% gratuity for services. A floorplan for the Illini Rooms in round tables is available in \textbf{Appendix D}.\\

### 2019-10-01 management.tex
grammar things + table

		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwen Chee)};
		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator\\(Roberto Fairhurst)};
		\node (sesh coord) [coordinator, below of = work coord, yshift = -2cm] {Sessions Coordinator (Zach Jeckell)};
		\node (cf coord) [coordinator, below of = sesh coord, yshift = -2cm] {Career Fair Coordinator (Greg Golba)};

@@

\subsection{Staffing Requirements}
Staffing for room breakdowns and setups, registration, socials, workshops, tours, etc.  will be supplied by either UIUC ANS members or students of the NPRE department. While it is likely that members of our student chapter will voluntarily fill all the staffing requirements of conference hosted events. If not, we will rely on other student organizations for support including, but not limited to: Arms Control and Domestic and International Security (ACDIS) and Women in Engineering (WIE). Participating in conference events on a staff level is a beneficial experience for any undergraduate who wants to become more familiar with ANS or support their ANS Chapter. Throughout the conference, interacting with registering students, driving groups to tour a scientific facility, and turning rooms for technical sessions provide plentiful opportunities for volunteers to interact with myriad members on a number of levels. Thus, it will be an overall positive experience for the volunteers. Quantitative needs are outlined in Appendix G on page \pageref{appendix:staff}.

>>>>

		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwendolyn Chee)};
		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator\\(Roberto Fairhurst)};
		\node (sesh coord) [coordinator, below of = work coord, yshift = -2cm] {Sessions Coordinator (Zach Jeckell)};
		\node (cf coord) [coordinator, below of = sesh coord, yshift = -2cm] {Career Fair Coordinator (Greg Golba)};

@@

\subsection{Staffing Requirements}
Staffing for room breakdowns and setups, registration, socials, workshops, 
tours, etc.  will be supplied by either UIUC ANS members or students of the 
NPRE department. While it is likely that members of our student chapter will 
voluntarily fill all the staffing requirements of conference hosted events. If 
not, we will rely on other student organizations for support including, but not 
limited to: Arms Control and Domestic and International Security (ACDIS) and 
Women in Engineering (WIE). Participating in conference events on a staff level 
is a beneficial experience for any undergraduate who wants to become more 
familiar with ANS or support their ANS Chapter. Throughout the conference, 
interacting with registering students, driving groups to tour a scientific 
facility, and turning rooms for technical sessions provide plentiful 
opportunities for volunteers to interact with myriad members on a number of 
levels. Thus, it will be an overall positive experience for the volunteers. 
Quantitative needs are outlined in Appendix \ref{appendix:staff} on page 
\pageref{appendix:staff}.

### 2019-10-01 uiuc.tex

\subsection{University of Illinois at Urbana-Champaign: Learning \& Labor}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.44\textwidth]{alma.jpg}
    \caption{Alma Mater accompanied by Learning and Labor}
  \end{center}
\end{wrapfigure}
Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions. The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs that came out of UIUC. The famous Morrow Plots, established in 1876, became the first research crop field at a university and is still used today. Attendees might also be familiar with Blue Waters, one of the world’s fastest supercomputers. 
The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics. Including John Bardeen, the only scientist to ever win the award in physics twice. It also offers 15 different majors to almost 6000 undergraduate and 2500 graduate students. Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree. Overall, the Grainger College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs. With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its nearly 45,000 students the ability to succeed.

\subsection{UIUC ANS Student Chapter (ANS-UIUC)}

The ANS-UIUC maintains and develops a cohesive community of students in nuclear 
engineering. It also engages in education and outreach programs to teach 
members of the surrounding community about nuclear science. One of our most 
popular outreach programs is Engineering Open House (EOH), during which 
ANS-UIUC repeatedly earns awards for best presentation of a society. EOH is an 
annual event where members of the local community, from young children to 
senior adults, visit the engineering campus to learn more about STEM research. 
Membership is currently around 70-80 students and has been steadily growing. 
The chapter works to host events catering to nuclear, plasma, and radiological 
concentrations. Professional development plays a crucial role in student 
development, and it is the biggest part of member involvement at UIUC. 
Professional development activities range from tours of various facilities to 
pizza with campus visitors. Some of the past tours have included Clinton Power 
Station, Curium Pharma through UIUC Women In Nuclear, Oak Ridge National 
Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory. 
ANS-UIUC has historically been one of the best represented institutions at the 
annual student conference and hosting it is a tradition this chapter is eager 
to uphold.

@@

\subsubsection{Plasma Physics and Fusion Science}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.48\textwidth]{hidra.png}
    \caption{The Hybrid Illinois Device for Research and Application (HIDRA)}
  \end{center}
\end{wrapfigure}
The Fusion and Plasma Physics research theme in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering. NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof. David Ruzic. Furthermore, in the past few years, two new faculty members have been added to this area including: Prof. Davide Curelli and Prof. Daniel Andruzcyk. There are five research themes that spans the work in fusion and plasma physics: fusion materials, plasma-material interface (PMI) diagnostics, plasma-edge and PMI modeling, plasma nanosynthesis, and plasma sources and processing. The Hybrid Illinois Device for Research and Application (HIDRA) marks the newest addition to the team at CPMI. This device finished construction and achieved first plasma during the spring of 2016. \\

>>>>

\subsection{University of Illinois at Urbana-Champaign: Learning \& Labor}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.44\textwidth]{alma.jpg}
    \caption{Alma Mater accompanied by Learning and Labor}
  \end{center}
\end{wrapfigure}
Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions. The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs that came out of UIUC. The famous Morrow Plots, established in 1876, became the first research crop field at a university and is still used today. Attendees might also be familiar with Blue Waters, one of the world’s fastest supercomputers. 
The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics, including John Bardeen, the only scientist to ever win the award in physics twice. It also offers 15 different majors to almost 6000 undergraduate and 2500 graduate students. Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree. Overall, the Grainger College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs. With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its nearly 45,000 students the ability to succeed.

\subsection{UIUC ANS Student Chapter (ANS-UIUC)}
The ANS-UIUC maintains and develops a cohesive community of students in nuclear 
engineering. It also engages in education and outreach programs to teach 
members of the surrounding community about nuclear science. One of our most 
popular outreach programs is Engineering Open House (EOH), during which 
ANS-UIUC repeatedly earns awards for best presentation of a society. EOH is an 
annual event where members of the local community, from young children to 
senior adults, visit the engineering campus to learn more about STEM research. 
Membership is currently around 70-80 students and has been steadily growing. 
The chapter works to host events catering to nuclear, plasma, and radiological 
concentrations. Professional development plays a crucial role in student 
development, and it is the biggest part of member involvement at UIUC. 
Professional development activities range from tours of various facilities to 
pizza with campus visitors. Some of the past tours have included Clinton Power 
Station, Curium Pharma through UIUC Women In Nuclear, Oak Ridge National 
Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory. 
ANS-UIUC has historically been one of the best represented institutions at the 
annual student conference and hosting it is a tradition this chapter is eager 
to uphold.

@@

\subsubsection{Plasma Physics and Fusion Science}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.48\textwidth]{hidra.png}
    \caption{The Hybrid Illinois Device for Research and Application (HIDRA)}
  \end{center}
\end{wrapfigure}
The Fusion and Plasma Physics research concentration in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering. NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof. David Ruzic. Furthermore, in the past few years, two new faculty members have been added to this area: Prof. Davide Curelli and Prof. Daniel Andruzcyk. There are five research themes that spans the work in fusion and plasma physics: fusion materials, plasma-material interface (PMI) diagnostics, plasma-edge and PMI modeling, plasma nanosynthesis, and plasma sources and processing. The Hybrid Illinois Device for Research and Application (HIDRA) marks the newest addition to the team at CPMI. This device finished construction and achieved first plasma during the spring of 2016. \\
